A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-31 main.tex
Extending \LTP with Dependent Types.

% CSP
CSP, cross-stage persistence is an important feature of multistage calculus.
\red{It enable us to embed value at an outer transition into an inner transition}.

@@

\subsection{\LLF}
\subsection{\LMD}

>>>>

% CSP
CSP, cross-stage persistence, is an important feature of multistage calculus.
\red{It enable us to embed value at an outer transition into an inner transition}.
$\%$ is dedicated for CSP in \LTP.
For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$

@@

There is another important function called program residualization in \LTP.
It means that a generated code can be dumped into a file.
We can load the dumped file and run it.
The difficulty is arise when program residualization is used with CSP.
Transition variables are classified to two kinds in \LTP in order to deal with this difficulty.

\subsection{Extending \LTP with Dependent Types}

Next, we develop \LMD by extending \LTP with dependent types.
